---
title: "Fitting ADBM to Broadstone Stream (size aggregation) food web"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(rdryad)
library(janitor)
library(tidyverse)
library(here)

source("https://raw.githubusercontent.com/opetchey/dumping_ground/master/ADBM_shiny/Plot.matrix.r")
source(here("R/ADBM.functions.r"))
```

# Introduction

This report shows how the allometric diet breadth model of [Petchey et al (2008)](https://www.pnas.org/content/105/11/4191) was fit to empirical food web data. The report is basic and unrefined (purely functional in purpose).

# Empirical data

## Broadstone Stream (size aggregation) data from Guy Woodward (2021)

The Broadstone Stream food web data was downloaded from [here](https://dx.doi.org/10.5281/zenodo.5575040) and then processed (steps are not shown in this document).

```{r warning = FALSE}
fw_name <- "Broadstone Stream size_agg"
broadstone_size_agg.openaccess.all.web.info <- readRDS(here(paste0("data/", fw_name, ".web.openaccess.RDS")))
Plot.matrix(broadstone_size_agg.openaccess.all.web.info$predation.matrix)
box()
```


# Fitting the model

## Starting parameter values

The search algorithm can get stuck in local optima, so the search is started multiple times each from a different location in parameter space. Those starting parameter values are loaded from a text file:

```{r}
ratio_initial_pars <- read.csv(here("data/ratio.initial.pars.txt"),
                               header = FALSE)
```


## Fit model to open access Broadstone Stream data

```{r eval = FALSE}
NM.RH.web_openaccess <- NM.ratio(broadstone_size_agg.openaccess.all.web.info, ratio_initial_pars)
```


```{r eval = FALSE, echo = FALSE}
saveRDS(NM.RH.web_openaccess,
        file=here(paste0("data/fitpar/", fw_name, "NMRHweb_openaccess.RDS")))
```

```{r echo = FALSE}
NM.RH.web_openaccess <- readRDS(file=here(paste0("data/fitpar/",
                                            fw_name, "NMRHweb_openaccess.RDS")))
```


```{r}
Plot.matrix(NM.RH.web_openaccess$web)
box()
NM.RH.web_openaccess$power
NM.RH.web_openaccess$pars
sum(NM.RH.web_openaccess$web)
sum(broadstone_size_agg.openaccess.all.web.info$predation.matrix)
Compare.links(NM.RH.web_openaccess$web, broadstone_size_agg.openaccess.all.web.info$predation.matrix)
```