---
title: "Fitting ADBM to Caricaie Lakes food web"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(rdryad)
library(janitor)
library(tidyverse)
library(here)

source("https://raw.githubusercontent.com/opetchey/dumping_ground/master/ADBM_shiny/Plot.matrix.r")
source(here("R/ADBM.functions.r"))
```

# Introduction

This report shows how the allometric diet breadth model of [Petchey et al. (2008)](https://www.pnas.org/content/105/11/4191) was fit to empirical food web data. The report is basic and unrefined (purely functional in purpose).

# Empirical data

## 2008 Caricaie Lakes

```{r}
fw_name <- "Caricaie Lakes"
caricaie2008.all.web.info <- readRDS(here(paste0("data/", fw_name, ".web.2008.RDS")))
Plot.matrix(caricaie2008.all.web.info$predation.matrix)
box()
```

## Caricaie Lakes data from Brose et al. (2008)

The Caricaie Lakes food web data was downloaded from [here](https://dx.doi.org/10.6084/m9.figshare.c.3298772) and then processed (steps are not shown in this document). The food web is exactly same as that used in Petchey et al. (2008).

```{r warning = FALSE}

caricaie.openaccess.all.web.info <- readRDS(here(paste0("data/", fw_name, ".web.openaccess.RDS")))
Plot.matrix(caricaie.openaccess.all.web.info$predation.matrix)
box()
```


# Fitting the model

## Starting parameter values

The search algorithm can get stuck in local optima, so the search is started multiple times each from a different location in parameter space. Those starting parameter values are loaded from a text file:

```{r}
ratio_initial_pars <- read.csv(here("data/ratio.initial.pars.txt"),
                               header = FALSE)
```


## Fit model to 2008 Caricaie Lakes data

Here the outcome is the same as in Petchey et al. (2008).

```{r eval = FALSE}
NM.RH.web_2008 <- NM.ratio(caricaie2008.all.web.info, ratio_initial_pars)
```

```{r eval = FALSE, echo = FALSE}
saveRDS(NM.RH.web_2008, file=here(paste0("data/fitpar/",
                                         fw_name, "NMRHweb_2008.RDS")))
```

```{r echo = FALSE}
NM.RH.web_2008 <- readRDS(file=here(paste0("data/fitpar/",
                                           fw_name, "NMRHweb_2008.RDS")))
```

```{r}
Plot.matrix(NM.RH.web_2008$web)
box()
NM.RH.web_2008$power
NM.RH.web_2008$pars
sum(NM.RH.web_2008$web)
sum(caricaie2008.all.web.info$predation.matrix)
```



## Fit model to open access Caricaie Lakes data

```{r eval = FALSE}
NM.RH.web_openaccess <- NM.ratio(caricaie.openaccess.all.web.info, ratio_initial_pars)
```


```{r eval = FALSE, echo = FALSE}
saveRDS(NM.RH.web_openaccess,
        file=here(paste0("data/fitpar/", fw_name, "NMRHweb_openaccess.RDS")))
```

```{r echo = FALSE}
NM.RH.web_openaccess <- readRDS(file=here(paste0("data/fitpar/",
                                            fw_name, "NMRHweb_openaccess.RDS")))
```


```{r}
Plot.matrix(NM.RH.web_openaccess$web)
box()
NM.RH.web_openaccess$power
NM.RH.web_openaccess$pars
sum(NM.RH.web_openaccess$web)
sum(caricaie.openaccess.all.web.info$predation.matrix)
Compare.links(NM.RH.web_openaccess$web, caricaie.openaccess.all.web.info$predation.matrix)
```




# Using 2008 parameter estimates

Using the 2008 parameter estimates gives the same results as in Petchey et al. (2008).

```{r}
a_2008 <- 3.27e-6
ai_2008 <- -4.67e-1
aj_2008 <- 5.39e-1
b_2008 <- 4.12e-2

EHL_2008 <- Ratio.allometric.EHL(M = caricaie2008.all.web.info$species.sizes,
                           e = 1,
                           r.a = 1, r.b = b_2008,
                           a = a_2008, ai = ai_2008, aj = aj_2008,
                           n = 1, ni=-3/4)
web_2008 <- Get.web(EHL_2008)
Plot.matrix(web_2008)
box()
Compare.links(web_2008, caricaie2008.all.web.info$predation.matrix)
```

