---
title: "Fitting ADBM to Grasslands food web"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(rdryad)
library(janitor)
library(tidyverse)
library(here)

source("https://raw.githubusercontent.com/opetchey/dumping_ground/master/ADBM_shiny/Plot.matrix.r")
source(here("R/ADBM.functions.r"))
```

# Introduction

This report shows how the allometric diet breadth model of [Petchey et al. (2008)](https://www.pnas.org/content/105/11/4191) was fit to empirical food web data. The report is basic and unrefined (purely functional in purpose).

# Empirical data

## 2008 Grasslands

```{r}
fw_name <- "Grasslands"
grasslands2008.all.web.info <- readRDS(here(paste0("data/", fw_name, ".web.2008.RDS")))
Plot.matrix(grasslands2008.all.web.info$predation.matrix)
box()
```

## Grasslands data from Brose et al. (2008)

The Grasslands food web data was downloaded from [here](https://dx.doi.org/10.6084/m9.figshare.c.3298772) and then processed (steps are not shown in this document). The food web is exactly same as that used in Petchey et al. (2008).

```{r warning = FALSE}

grasslands.openaccess.all.web.info <- readRDS(here(paste0("data/", fw_name, ".web.openaccess.RDS")))
Plot.matrix(grasslands.openaccess.all.web.info$predation.matrix)
box()
```


# Fitting the model

The Nelder-Mead method does not converge for the Grasslands food web. 